---
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# UHHformats

This R package provides ready-to-use **R Markdown** and **Quarto** templates for HTML, PDF, and Microsoft Word output formats. The templates are designed for the Department of Biology, University of Hamburg (UHH), and its *Data Science in Biology* program, but can be used by anyone --- logos and styles are easily customizable via the YAML header.

All templates ship with example text and code for formatting, equations, tables, figures with cross-references, and citations.

> For thesis templates see the companion package [UHHthesis](https://github.com/uham-bio/UHHthesis) or the separate [Quarto extension](https://github.com/uham-bio/quarto-UHHthesis).

## Available templates

| Template | R Markdown function | Quarto template |
|:---------|:--------------------|:----------------|
| HTML document | `html_doc()` | `html_doc` |
| Simple PDF document | `pdf_doc()` | `pdf_doc` |
| PDF report | `pdf_report()` | `pdf_report` |
| PDF cheat sheet | `pdf_cheatsheet()` | `pdf_cheatsheet` |
| Word document | `word_doc()` | `word_doc` |

The default font is Helvetica. PDF and Word templates also support the University's own font TheSans UHH (available to UHH members).

> **Backward compatibility:** The old function names `html_simple()` and `pdf_simple()` still work as aliases.

## Installation

Install from GitHub:

```{r, eval = FALSE}
# Using the package 'pak' (recommended)
if (!require("pak")) install.packages("pak")
pak::pak("uham-bio/UHHformats")

# Alternatively, using 'remotes'
if (!require("remotes")) install.packages("remotes")
remotes::install_github("uham-bio/UHHformats", build_vignettes = TRUE)
```

Required dependencies (rmarkdown, knitr, bookdown) are installed automatically.

## Prerequisites

### Quarto CLI

For Quarto templates, install the [Quarto CLI](https://quarto.org/docs/get-started/). To render `.qmd` files from R, also install the quarto R package:

```{r, eval = FALSE}
install.packages("quarto")
```

### Pandoc

R Markdown and Quarto use [Pandoc](https://pandoc.org/) to convert documents. RStudio ships with its own Pandoc installation. If you render from the console without RStudio, you need Pandoc installed on your system:

- Installation: <https://pandoc.org/installing.html>
- Minimum required version: 2.17

### LaTeX (for PDF output)

For PDF output you also need a LaTeX distribution. An easy cross-platform option is the [tinytex](https://yihui.org/tinytex/) R package:

```{r, eval = FALSE}
install.packages("tinytex")
tinytex::install_tinytex()
```

For other distributions see <https://www.latex-project.org/get/>.

---

## Learn more

- [Getting started (EN)](articles/UHHformats.html) — quick walkthrough of all templates
- [Erste Schritte (DE)](articles/UHHformats-de.html) — deutschsprachige Einführung
- [Template gallery](articles/gallery.html) — screenshots and demo files for all templates

---

## Useful resources

- R Markdown
    - The official [R Markdown documentation](https://rmarkdown.rstudio.com/lesson-1.html) from RStudio
    - R Markdown [reference guide](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)
    - R Markdown [cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf)
    - The online book [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/) by Yihui Xie, J. J. Allaire, and Garrett Grolemund
- Quarto
    - The official [Quarto guide](https://quarto.org/docs/guide/)
    - Quarto's [Gallery](https://quarto.org/docs/gallery/)
- LaTeX
    - The official [LaTeX help and documentation](https://www.latex-project.org/help/documentation/)
    - The [overleaf](https://www.overleaf.com/learn) documentation
- W3Schools Online Web Tutorial for [HTML](https://www.w3schools.com/html/default.asp) and for [CSS](https://www.w3schools.com/css/default.asp)
