---
title: "Template gallery"
output: rmarkdown::html_vignette
description: >
  Screenshots and demo files for all UHHformats R Markdown and Quarto templates.
vignette: >
  %\VignetteIndexEntry{Template gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
base_url <- "https://github.com/uham-bio/UHHformats/raw/master/resources/examples"
```

Each template ships with example content covering text formatting, equations, tables, figures with cross-references, and citations. Click **Download demo** to get a ready-to-open example file.

---

## R Markdown templates

### HTML document (*html_doc*)

A self-contained HTML page with a fixed table of contents, code folding, and lightbox image display. Uses `bookdown::html_document2` for automatic figure/table numbering and cross-references.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_rmd_html_doc.png",
    alt = "html_doc template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (HTML)](`r paste0(base_url, "/demo_rmd_html_doc.html")`){.btn .btn-outline-primary .btn-sm}

---

### Simple PDF document (*pdf_doc*)

A clean PDF article suitable for student assignments. Supports English and German, customisable logos and header/footer.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_rmd_pdf_doc.png",
    alt = "pdf_doc template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (PDF)](`r paste0(base_url, "/demo_rmd_pdf_doc.pdf")`){.btn .btn-outline-primary .btn-sm}

---

### PDF report (*pdf_report*)

A report-style PDF with a cover page, header/footer, and table of contents. Suitable for project reports and course work.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_rmd_pdf_report.png",
    alt = "pdf_report template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (PDF)](`r paste0(base_url, "/demo_rmd_pdf_report.pdf")`){.btn .btn-outline-primary .btn-sm}

---

### PDF cheat sheet (*pdf_cheatsheet*)

A landscape A4 cheat sheet with configurable columns, coloured text boxes, and adjustable font sizes.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_rmd_pdf_cheatsheet.png",
    alt = "pdf_cheatsheet template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (PDF)](`r paste0(base_url, "/demo_rmd_pdf_cheatsheet.pdf")`){.btn .btn-outline-primary .btn-sm}

---

### Word document (*word_doc*)

A Microsoft Word document using the UHH corporate design. Supports automatic language switching for figure and table captions.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_rmd_word_doc.png",
    alt = "word_doc template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (DOCX)](`r paste0(base_url, "/demo_rmd_word_doc.docx")`){.btn .btn-outline-primary .btn-sm}

---

## Quarto templates

### HTML document (*html_doc*)

A Quarto HTML page with navigation bar and UHH logo. Supports all standard Quarto HTML features including tabsets, callouts, and interactive widgets.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_quarto_html_doc.png",
    alt = "Quarto html_doc template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (HTML)](`r paste0(base_url, "/demo_quarto_html.html")`){.btn .btn-outline-primary .btn-sm}

---

### Simple PDF document (*pdf_doc*)

A Quarto PDF document in the same style as the R Markdown `pdf_doc` template, using the KOMA-Script article class and XeLaTeX.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_quarto_pdf_doc.png",
    alt = "Quarto pdf_doc template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (PDF)](`r paste0(base_url, "/demo_quarto_pdf_doc.pdf")`){.btn .btn-outline-primary .btn-sm}

---

### PDF report (*pdf_report*)

A Quarto report-style PDF with a customisable cover page, title page, logos, and table of contents. Cover appearance (image, colours, fade effect) can be controlled via YAML.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_quarto_pdf_report.png",
    alt = "Quarto pdf_report template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (PDF)](`r paste0(base_url, "/demo_quarto_pdf_report.pdf")`){.btn .btn-outline-primary .btn-sm}

---

### PDF cheat sheet (*pdf_cheatsheet*)

A Quarto-based cheat sheet with configurable columns, coloured text boxes, and adjustable font sizes (see the R Markdown equivalent above for a visual comparison).

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_quarto_pdf_cheatsheet.png",
    alt = "Quarto pdf_cheatsheet template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (PDF)](`r paste0(base_url, "/demo_quarto_pdf_cheatsheet.pdf")`){.btn .btn-outline-primary .btn-sm}

---

### Word document (*word_doc*)

A Quarto Word document using the UHH corporate design template with Helvetica or TheSans UHH font.

```{r}
htmltools::tags$figure(
  htmltools::tags$img(
    src = "images/img_quarto_word_doc.png",
    alt = "Quarto word_doc template screenshot",
    style = "width:60%; border: 1px solid #ddd; border-radius: 4px;"
  )
)
```

[Download demo (DOCX)](`r paste0(base_url, "/demo_quarto_word_doc.docx")`){.btn .btn-outline-primary .btn-sm}
